---
title: "pediatric ADE performance with generated negatives"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = F,message = F,
                      fig.width = 10)
```

#### load libraries

```{r}

library(tidyverse)
library(data.table)

theme_set(
  theme_classic(base_size = 16) +
    theme(
      text = element_text(face="bold")
    )
  )

library(doParallel)
registerDoParallel(cores=4)
```

#### set variables

```{r}

level <- "pt"
out_dir <- "../docs/imgs/"
basename <- paste0("pediatric_reference_",level,"_ADE_performances_with_generated_negatives")

```

## load data

```{r}

truth_all <- fread(paste0("../data/GRiP_Pediatric_ADE_with_generated_negatives_meddra",level,".csv"))

count <- fread(paste0("../data/pediatric_reference_",level,"_ADEs_counts_contigency_table_tests.csv"))

psm_prr <- fread(paste0("../data/pediatric_reference_",level,"_all_and_nichd_psm_prr.csv"))
psm_prr = psm_prr[DE>0 & psm_prr$nichd==""]

glm_rx_drug_psd_cunder <- fread(paste0("../data/pediatric_reference_",level,"_ADE_glm_with_drug_or_PSd_control_undersampling.csv"),drop = c("V1"))

glm_rx_all_drugs_cunder <- fread(paste0("../data/pediatric_reference_",level,"_ADE_glm_with_drugs_control_undersampling.csv"),drop = c("V1"))

glm_rx_drug_cunder <- 
  glm_rx_drug_psd_cunder[
  model_id=="fd_5cv"]

glm_rx_drug_cunder$atc_concept_id <- as.integer(glm_rx_drug_cunder$atc_concept_id)

glm_rx_drug_cunder$meddra_concept_id <- as.integer(glm_rx_drug_cunder$meddra_concept_id)




glm_rx_PSd_cunder <- 
  glm_rx_drug_psd_cunder[
  model_id=="fPSd_5cv"]

glm_rx_PSd_cunder$atc_concept_id <- sapply(strsplit(glm_rx_PSd_cunder$atc_concept_id,"_"),function(x){x[1]})

glm_rx_PSd_cunder$atc_concept_id <- as.integer(glm_rx_PSd_cunder$atc_concept_id)

glm_rx_PSd_cunder$meddra_concept_id <- as.integer(glm_rx_PSd_cunder$meddra_concept_id)



glm_rx_all_drugs_cunder <- 
  glm_rx_all_drugs_cunder[
  model_id=="fdrugs_5cv"]

glm_rx_all_drugs_cunder$atc_concept_id <- as.integer(glm_rx_all_drugs_cunder$atc_concept_id)

glm_rx_all_drugs_cunder$meddra_concept_id <- as.integer(glm_rx_all_drugs_cunder$meddra_concept_id)


```

```{r}

truth_pred_join <- read_csv(paste0("../data/pediatric_reference_",level,"_ADEs_counts_contigency_table_tests.csv")) %>% 
  filter(a>0) %>% 
  data.table()

truth_pred_psm_prr_no_cunder_join <- inner_join(truth_all,psm_prr,
                   by=c("ATC_concept_id"="atc_concept_id",
                        "MedDRA_concept_id"="meddra_concept_id")
                   ) %>% 
  select(ATC_concept_name,MedDRA_concept_name,
         Control,
         PRR) %>% 
  distinct() %>% 
  data.table()

truth_glm_rx_PSd_cunder_join <- inner_join(truth_all,glm_rx_PSd_cunder,
                   by=c("ATC_concept_id"="atc_concept_id",
                        "MedDRA_concept_id"="meddra_concept_id")
                   ) %>% 
  select(ATC_concept_name,MedDRA_concept_name,
         Control,bootstrap,
         coefficient) %>% 
  distinct() %>% 
  group_by(ATC_concept_name,MedDRA_concept_name,
         Control) %>% 
  mutate(
    sdest = sd(coefficient),
    mest = mean(coefficient),
    lwr = mest - sdest,
    upr = mest + sdest
  ) %>% 
  ungroup() %>% 
  select(-bootstrap,-coefficient,-sdest) %>% 
  data.table()

truth_glm_rx_d_cunder_join <- inner_join(truth_all,glm_rx_drug_cunder,
                   by=c("ATC_concept_id"="atc_concept_id",
                        "MedDRA_concept_id"="meddra_concept_id")
                   ) %>% 
  select(ATC_concept_name,MedDRA_concept_name,
         Control,bootstrap,
         coefficient) %>% 
  distinct()  %>% 
  group_by(ATC_concept_name,MedDRA_concept_name,
         Control) %>% 
  mutate(
    sdest = sd(coefficient),
    mest = mean(coefficient),
    lwr = mest - sdest,
    upr = mest + sdest
  ) %>% 
  ungroup() %>% 
  select(-bootstrap,-coefficient,-sdest) %>% 
  data.table()

truth_glm_rx_ds_cunder_join <- inner_join(truth_all,glm_rx_all_drugs_cunder,
                   by=c("ATC_concept_id"="atc_concept_id",
                        "MedDRA_concept_id"="meddra_concept_id")
                   ) %>% 
  select(ATC_concept_name,MedDRA_concept_name,
         Control,bootstrap,
         coefficient) %>% 
  distinct() %>% 
  group_by(ATC_concept_name,MedDRA_concept_name,
         Control) %>% 
  mutate(
    sdest = sd(coefficient),
    mest = mean(coefficient),
    lwr = mest - sdest,
    upr = mest + sdest
  ) %>% 
  ungroup() %>% 
  select(-bootstrap,-coefficient,-sdest) %>% 
  data.table()

```

```{r}

table(truth_pred_join$Control)

```

## Define performance functions

```{r}

vary_phv_threshold <- function(joined,
                               n,
                               param="",
                               drug_col="",rx_col=""){

  tp_cond = paste0(param," > ",n," & Control=='P'")
  fp_cond = paste0(param," > ",n," & Control=='N'")
  fn_cond = paste0(param," <= ",n," & Control=='P'")
  tn_cond = paste0(param," <= ",n," & Control=='N'")
  
  tps <- joined %>% 
    filter_(tp_cond)
  fps <- joined %>% 
    filter_(fp_cond)
  fns <- joined %>% 
    filter_(fn_cond)  
  tns <- joined %>% 
    filter_(tn_cond)
  
  tp_num = tps %>% 
    select(!!drug_col,!!rx_col) %>% 
    n_distinct()
  
  fp_num = fps %>% 
    select(!!drug_col,!!rx_col) %>% 
    n_distinct()
  
  fn_num = fns %>% 
    select(!!drug_col,!!rx_col) %>% 
    n_distinct()

  tn_num = tns %>% 
    select(!!drug_col,!!rx_col) %>% 
    n_distinct()
  
  df <- data.frame(
    "TP" = tp_num,
    "FP" = fp_num,
    "FN" = fn_num,
    "TN" = tn_num,
    "Threshold" = as.numeric(n),
    "Stat" = param
  ) 
  
  df
  
}

```



## Compare statistic performance

```{r}

thresholds <- c(0,unique(truth_pred_join$a),1)
thresholds <- thresholds[order(thresholds,decreasing = F)]
thresholds <- thresholds[!is.infinite(thresholds)]

df_count <- do.call(rbind,
              lapply(thresholds,
                     function(x){
                       vary_phv_threshold(
                         truth_pred_join,
                         x,
                         param="a",
                         drug_col="ATC_concept_name",
                         rx_col="MedDRA_concept_name"
                         )
                     }
              )
)
df_count["Statistic"] <- "Number of Reports"

g <- 
  bind_rows(
    df_count
) %>%  
  group_by(Statistic) %>% 
  mutate(
    Sensitivity = TP / (TP + FN),
    Specificity = (FP / (FP + TN))
  ) %>%
  ungroup() %>% 
  ggplot(aes(Specificity,Sensitivity,color=Statistic)) +
  scale_color_brewer(palette="Set1") +
  geom_point() +
  geom_line() +
  ylab("Sensitivity") +
  xlab("1 - Specificity") +
  xlim(0,1) +
  ylim(0,1)
  
print(g)

ggsave(paste0(out_dir,basename,"_ROC_performance_counts.png"),
       width=10,height=5)
g <- 
  bind_rows(
    df_count
) %>%  
  group_by(Statistic) %>% 
  mutate(
    Precision = TP / (TP + FP),
    Recall = (TP / (FN + TP))
  ) %>%
  ungroup() %>% 
  ggplot(aes(Recall,Precision,color=Statistic)) +
  scale_color_brewer(palette="Set1") +
  geom_point() +
  geom_line() +
  ylab("Precision") +
  xlab("Recall") +
  xlim(0,1) +
  ylim(0,1)
  
print(g)

ggsave(paste0(out_dir,basename,"_ROC_precision_recall_counts.png"),
       width=10,height=5)

thresholds <- c(0,unique(truth_pred_join$PRR),1)
thresholds <- thresholds[order(thresholds,decreasing = F)]
thresholds <- thresholds[!is.infinite(thresholds)]

df_prr <- do.call(rbind,
              lapply(thresholds,
                     function(x){
                       vary_phv_threshold(
                         truth_pred_join,
                         x,
                         param="PRR",
                         drug_col="ATC_concept_name",
                         rx_col="MedDRA_concept_name"
                         )
                     }
              )
)
df_prr["Statistic"] <- "PRR"

g <- 
  bind_rows(
    df_count,
    df_prr
) %>%  
  group_by(Statistic) %>% 
  mutate(
    Sensitivity = TP / (TP + FN),
    Specificity = (FP / (FP + TN))
  ) %>%
  ungroup() %>% 
  ggplot(aes(Specificity,Sensitivity,color=Statistic)) +
  scale_color_brewer(palette="Set1") +
  geom_point() +
  geom_line() +
  ylab("Sensitivity") +
  xlab("1 - Specificity") +
  xlim(0,1) +
  ylim(0,1)
  
print(g)

ggsave(paste0(out_dir,basename,"_ROC_performance_counts_prr.png"),
       width=10,height=5)
g <- 
  bind_rows(
    df_count,
    df_prr
) %>%  
  group_by(Statistic) %>% 
  mutate(
    Precision = TP / (TP + FP),
    Recall = (TP / (FN + TP))
  ) %>%
  ungroup() %>% 
  ggplot(aes(Recall,Precision,color=Statistic)) +
  scale_color_brewer(palette="Set1") +
  geom_point() +
  geom_line() +
  ylab("Precision") +
  xlab("Recall") +
  xlim(0,1) +
  ylim(0,1)
  
print(g)

ggsave(paste0(out_dir,basename,"_ROC_precision_recall_counts_prr.png"),
       width=10,height=5)

df_psm_prr <- do.call(rbind,
              lapply(thresholds,
                     function(x){
                       vary_phv_threshold(
                         truth_pred_psm_prr_no_cunder_join,
                         x,
                         param="PRR",
                         drug_col="ATC_concept_name",
                         rx_col="MedDRA_concept_name"
                         )
                     }
              )
)
df_psm_prr["Statistic"] <- "PSM PRR"

thresholds <- c(0,unique(truth_glm_rx_d_cunder_join$mest),1)
thresholds <- thresholds[order(thresholds,decreasing = F)]
thresholds <- thresholds[!is.infinite(thresholds)]

df_rxn_d <- do.call(rbind,
              lapply(thresholds,
                     function(x){
                       vary_phv_threshold(
                         truth_glm_rx_d_cunder_join,
                         x,
                         param="mest",
                         drug_col="ATC_concept_name",
                         rx_col="MedDRA_concept_name"
                         )
                     }
              )
)
df_rxn_d["Statistic"] <- "drug"

thresholds <- c(0,unique(truth_glm_rx_PSd_cunder_join$mest),1)
thresholds <- thresholds[order(thresholds,decreasing = F)]
thresholds <- thresholds[!is.infinite(thresholds)]

df_rxn_PSd <- do.call(rbind,
              lapply(thresholds,
                     function(x){
                       vary_phv_threshold(
                         truth_glm_rx_PSd_cunder_join,
                         x,
                         param="mest",
                         drug_col="ATC_concept_name",
                         rx_col="MedDRA_concept_name"
                         )
                     }
              )
)
df_rxn_PSd["Statistic"] <- "propensity score"

thresholds <- c(0,unique(truth_glm_rx_ds_cunder_join$mest),1)
thresholds <- thresholds[order(thresholds,decreasing = F)]
thresholds <- thresholds[!is.infinite(thresholds)]

df_rxn_ds <- do.call(rbind,
              lapply(thresholds,
                     function(x){
                       vary_phv_threshold(
                         truth_glm_rx_ds_cunder_join,
                         x,
                         param="mest",
                         drug_col="ATC_concept_name",
                         rx_col="MedDRA_concept_name"
                         )
                     }
              )
)
df_rxn_ds["Statistic"] <- "drug | all other drugs"


g <- 
  bind_rows(
    df_count,
    df_prr,
    df_psm_prr,
    df_rxn_d,
    df_rxn_PSd,
    df_rxn_ds
) %>%  
  group_by(Statistic) %>% 
  mutate(
    Sensitivity = TP / (TP + FN),
    Specificity = (FP / (FP + TN))
  ) %>%
  ungroup() %>% 
  ggplot(aes(Specificity,Sensitivity,color=Statistic)) +
  scale_color_brewer(palette="Set1") +
  geom_point() +
  geom_line() +
  ylab("Sensitivity") +
  xlab("1 - Specificity") +
  xlim(0,1) +
  ylim(0,1)
  
print(g)

ggsave(paste0(out_dir,basename,"_ROC_performance_comparison.png"),
       width=10,height=5)
g <- 
  bind_rows(
    df_count,
    df_prr,
    df_psm_prr,
    df_rxn_d,
    df_rxn_PSd,
    df_rxn_ds
) %>%  
  group_by(Statistic) %>% 
  mutate(
    Precision = TP / (TP + FP),
    Recall = (TP / (FN + TP))
  ) %>%
  ungroup() %>% 
  ggplot(aes(Recall,Precision,color=Statistic)) +
  scale_color_brewer(palette="Set1") +
  geom_point() +
  geom_line() +
  ylab("Precision") +
  xlab("Recall") +
  xlim(0,1) +
  ylim(0,1)
  
print(g)

ggsave(paste0(out_dir,basename,"_ROC_precision_recall_comparison.png"),
       width=10,height=5)

```

### Scores

```{r}

df <- bind_rows(
  df_count,
  df_prr,
  df_psm_prr,
  df_rxn_d,
  df_rxn_PSd,
  df_rxn_ds
) %>%  
  arrange(Threshold) %>% 
  group_by(Statistic) %>% 
  mutate(
    TPR = (TP / (TP + FN)),
    FPR = (FP / (FP + TN)),
    FNR = (FN / (FN + TP)),
    FDR = (FP / (FP + TP)),
    PPV = (TP / (TP + FP)),
    NPV = (TN / (TN + FN)),
    TNR = (TN / (TN + FP))
  )

simple_auc <- function(TPR, FPR){
  # inputs already sorted, best scores first 
  dFPR <- c(diff(FPR), 0)
  dTPR <- c(diff(TPR), 0)
  sum(TPR * dFPR) + sum(dTPR * dFPR)/2
}

df_scores <- NULL
for(stat in unique(df$Statistic)){
  tmp <- df %>% filter(Statistic==stat) %>% drop_na()
  tpr <- tmp$TPR[order(tmp$TPR)]
  fpr <- tmp$FPR[order(tmp$FPR)]
  df_scores <- rbind(df_scores,c(stat,"AUROC",simple_auc(tpr,fpr)))
}

for(stat in unique(df$Statistic)){
  tmp <- df %>% filter(Statistic==stat) %>% drop_na()
  recall <- tmp$TPR[order(tmp$TPR)]
  precision <- tmp$PPV[order(tmp$PPV)]
  df_scores <- rbind(df_scores,c(stat,"AUPRC",simple_auc(recall,precision)))
}

df_scores <- as_tibble(df_scores,.name_repair = "minimal")
colnames(df_scores) <- c("Detection","Metric","Score")
df_scores$Score <- as.numeric(df_scores$Score)

g <- df_scores %>% 
  ggplot(aes(forcats::fct_reorder(Detection,Score),Score,fill=Detection)) +
  geom_bar(stat="identity") +
  scale_fill_brewer(palette = "Set1") +
  geom_text(aes(label=round(Score,2)),hjust=-.2,fontface="bold") +
  facet_grid(Metric~.) +
  xlab("") +
  ylim(0,1) +
  coord_flip() +
  theme(
    legend.position = "none"
  )

print(g)

ggsave(paste0(out_dir,basename,"_aumetric_performances_comparison.png"),
       width=10,height=5)

g <- df %>% 
  gather(Metric, Value,
         -Threshold,-Statistic) %>% 
  filter(!(Metric %in% c("TP","TN","FP","FN"))) %>% 
  ggplot(aes(Threshold,Value,
                 color=Statistic,
                 group=Statistic)) +
  geom_point() +
  geom_path() +
  facet_wrap(~Metric) +
  scale_color_brewer(palette="Set1") +
  scale_x_log10()


print(g)

ggsave(paste0(out_dir,basename,"_metric_performances_comparison.png"),
       width=10,height=5)

g <- df %>% 
  gather(Metric, Value,
         -Threshold,-Statistic) %>% 
  filter((Metric %in% c("PPV","TPR"))) %>% 
  ggplot(aes(Threshold,Value,
                 color=Statistic,
                 group=Statistic)) +
  geom_point() +
  geom_path() +
  facet_wrap(~Metric) +
  scale_color_brewer(palette="Set1") +
  scale_x_log10()


print(g)

ggsave(paste0(out_dir,basename,"_PPV_TPR_performance_comparison.png"),
       width=10,height=5)

g <- df %>% 
  gather(Metric, Value,
         -Threshold,-Statistic) %>% 
  filter((Metric %in% c("PPV","NPV","FPR","TPR"))) %>% 
  ggplot(aes(Threshold,Value,
                 color=Metric,
                 group=Metric)) +
  geom_point() +
  geom_path() +
  facet_wrap(~Statistic) +
  scale_color_brewer(palette="Set1") +
  scale_x_log10()


print(g)

ggsave(paste0(out_dir,basename,"_statistic_performances_comparison.png"),
       width=10,height=5)
```

## Evaluate metrics against parameter

### number of reports

```{r}

drug_col <- "ATC_concept_name"
rx_col <- "MedDRA_concept_name"


g <- inner_join(
  truth_pred_join[,c(drug_col,rx_col,"a","Control"),with=F],
  truth_pred_psm_prr_no_cunder_join[,c(drug_col,rx_col,"PRR"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(PRR_PSM = PRR) %>% 
  inner_join(
  truth_pred_join[,c(drug_col,rx_col,"PRR"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  gather(detection,value,-drug_col,-rx_col,-a,-Control) %>% 
  filter(detection!="PRR_PSM") %>% 
  ggplot(aes(a,value)) + 
  geom_point(aes(fill=Control), 
       colour="black",pch=21, size=2) +
  geom_smooth(aes(group=Control)) +
  scale_fill_brewer(palette="Set1") +
  facet_wrap(~detection) +
  scale_x_log10() +
  scale_y_log10() +
  xlab("Number of Reports\n(log10)") +
  ylab("PRR\n(log10)")

print(g)

ggsave(paste0(out_dir,basename,"_prr_count_correlation.png"),
       width=10,height=5)

g <- inner_join(
  truth_pred_join[,c(drug_col,rx_col,"a","Control"),with=F],
  truth_pred_psm_prr_no_cunder_join[,c(drug_col,rx_col,"PRR"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  gather(detection,value,-drug_col,-rx_col,-a,-Control) %>% 
  ggplot(aes(a,value)) + 
  geom_point(aes(fill=Control), 
       colour="black",pch=21, size=2) +
  geom_smooth(aes(group=Control)) +
  scale_fill_brewer(palette="Set1") +
  facet_wrap(~detection) +
  scale_x_log10() +
  scale_y_log10() +
  xlab("Number of Reports\n(log10)") +
  ylab("PRR\n(log10)")

print(g)

ggsave(paste0(out_dir,basename,"_prr_count_correlation.png"),
       width=10,height=5)

g <- inner_join(
  truth_pred_join[,c(drug_col,rx_col,"a","Control"),with=F],
  truth_pred_psm_prr_no_cunder_join[,c(drug_col,rx_col,"PRR"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(PRR_PSM = PRR) %>% 
  inner_join(
  truth_pred_join[,c(drug_col,rx_col,"PRR"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  inner_join(
  truth_glm_rx_d_cunder_join[,c(drug_col,rx_col,"mest"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(drug = mest) %>%  
  inner_join(
  truth_glm_rx_ds_cunder_join[,c(drug_col,rx_col,"mest"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(drug_given_all_drugs = mest) %>% 
  gather(detection,value,-drug_col,-rx_col,-a,-Control) %>% 
  filter(detection=="drug") %>% 
  ggplot(aes(a,value)) + 
  geom_point(aes(fill=Control), 
       colour="black",pch=21, size=2) +
  geom_smooth(aes(group=detection)) +
  scale_fill_brewer(palette="Set1") +
  facet_wrap(~detection) +
  scale_x_log10()

print(g)

g <- inner_join(
  truth_pred_join[,c(drug_col,rx_col,"a","Control"),with=F],
  truth_pred_psm_prr_no_cunder_join[,c(drug_col,rx_col,"PRR"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(PRR_PSM = PRR) %>% 
  inner_join(
  truth_pred_join[,c(drug_col,rx_col,"PRR"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  inner_join(
  truth_glm_rx_d_cunder_join[,c(drug_col,rx_col,"mest"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(drug = mest) %>%  
  inner_join(
  truth_glm_rx_ds_cunder_join[,c(drug_col,rx_col,"mest"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(drug_given_all_drugs = mest) %>% 
  gather(detection,value,-drug_col,-rx_col,-a,-Control) %>% 
  filter(detection=="drug_given_all_drugs" | 
           detection=="drug") %>% 
  ggplot(aes(a,value)) + 
  geom_point(aes(fill=Control), 
       colour="black",pch=21, size=2) +
  geom_smooth(aes(group=Control)) +
  scale_fill_brewer(palette="Set1") +
  facet_wrap(~detection) +
  scale_x_log10()

print(g)

ggsave(paste0(out_dir,basename,"_glm_drug_and_allotherdrugs_correlation.png"),
       width=10,height=5)

inner_join(
  truth_pred_join[,c(drug_col,rx_col,"a","Control"),with=F],
  truth_pred_psm_prr_no_cunder_join[,c(drug_col,rx_col,"PRR"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(PRR_PSM = PRR) %>% 
  inner_join(
  truth_pred_join[,c(drug_col,rx_col,"PRR"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  inner_join(
  truth_glm_rx_d_cunder_join[,c(drug_col,rx_col,"mest"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(drug = mest) %>%  
  inner_join(
  truth_glm_rx_ds_cunder_join[,c(drug_col,rx_col,"mest"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(drug_given_all_drugs = mest) %>% 
  gather(detection,value,-drug_col,-rx_col,-a,-Control) %>% 
  ggplot(aes(a,value)) + 
  geom_point(aes(fill=Control), 
       colour="black",pch=21, size=2) +
  geom_smooth(aes(group=detection)) +
  scale_fill_brewer(palette="Set1") +
  facet_wrap(~detection) +
  scale_x_log10()

inner_join(
  truth_pred_join[,c(drug_col,rx_col,"a","Control"),with=F],
  truth_pred_psm_prr_no_cunder_join[,c(drug_col,rx_col,"PRR"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(PRR_PSM = PRR) %>% 
  inner_join(
  truth_pred_join[,c(drug_col,rx_col,"PRR"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  inner_join(
  truth_glm_rx_d_cunder_join[,c(drug_col,rx_col,"mest"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(drug = mest) %>%  
  inner_join(
  truth_glm_rx_ds_cunder_join[,c(drug_col,rx_col,"mest"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(drug_given_all_drugs = mest) %>% 
  gather(detection,value,-drug_col,-rx_col,-a,-Control) %>% 
  ggplot(aes(a,value)) + 
  geom_point(aes(fill=Control), 
       colour="black",pch=21, size=2) +
  geom_smooth(aes(group=detection)) +
  scale_fill_brewer(palette="Set1") +
  facet_wrap(~detection) +
  scale_y_log10()

inner_join(
  truth_pred_join[,c(drug_col,rx_col,"a","Control"),with=F],
  truth_pred_psm_prr_no_cunder_join[,c(drug_col,rx_col,"PRR"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(PRR_PSM = PRR) %>% 
  inner_join(
  truth_pred_join[,c(drug_col,rx_col,"PRR"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  inner_join(
  truth_glm_rx_d_cunder_join[,c(drug_col,rx_col,"mest"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(drug = mest) %>%  
  inner_join(
  truth_glm_rx_ds_cunder_join[,c(drug_col,rx_col,"mest"),with=F],
  by=c(drug_col,rx_col)
  ) %>% 
  rename(drug_given_all_drugs = mest) %>% 
  gather(detection,value,-drug_col,-rx_col,-a,-Control) %>% 
  ggplot(aes(a,value)) + 
  geom_point(aes(fill=Control), 
       colour="black",pch=21, size=2) +
  geom_smooth(aes(group=detection)) +
  scale_fill_brewer(palette="Set1") +
  facet_wrap(~detection) +
  scale_x_log10() +
  scale_y_log10()


```


## data for inspection

```{r}

df_count

df_prr

df_psm_prr

df_rxn_d

df_rxn_PSd

df_rxn_ds

```

## Cutoffs

```{r}

df_a_metrics <- df_count %>% 
  mutate(
    TPR = (TP / (TP + FN)),
    FPR = (FP / (FP + TN)),
    FNR = (FN / (FN + TP)),
    FDR = (FP / (FP + TP)),
    PPV = (TP / (TP + FP)),
    NPV = (TN / (TN + FN)),
    TNR = (TN / (TN + FP))  
    )

df_prr_metrics <- df_prr %>% 
  mutate(
    TPR = (TP / (TP + FN)),
    FPR = (FP / (FP + TN)),
    FNR = (FN / (FN + TP)),
    FDR = (FP / (FP + TP)),
    PPV = (TP / (TP + FP)),
    NPV = (TN / (TN + FN)),
    TNR = (TN / (TN + FP))  
    )

df_psm_prr_metrics <- df_psm_prr %>% 
  mutate(
    TPR = (TP / (TP + FN)),
    FPR = (FP / (FP + TN)),
    FNR = (FN / (FN + TP)),
    FDR = (FP / (FP + TP)),
    PPV = (TP / (TP + FP)),
    NPV = (TN / (TN + FN)),
    TNR = (TN / (TN + FP))  
    )

df_rxn_PSd_cunder_metrics <- df_rxn_PSd %>% 
  mutate(
    TPR = (TP / (TP + FN)),
    FPR = (FP / (FP + TN)),
    FNR = (FN / (FN + TP)),
    FDR = (FP / (FP + TP)),
    PPV = (TP / (TP + FP)),
    NPV = (TN / (TN + FN)),
    TNR = (TN / (TN + FP))  
    )

df_rxn_d_cunder_metrics <- df_rxn_d %>% 
  mutate(
    TPR = (TP / (TP + FN)),
    FPR = (FP / (FP + TN)),
    FNR = (FN / (FN + TP)),
    FDR = (FP / (FP + TP)),
    PPV = (TP / (TP + FP)),
    NPV = (TN / (TN + FN)),
    TNR = (TN / (TN + FP))  
    )

df_rxn_ds_cunder_metrics <- df_rxn_ds %>% 
  mutate(
    TPR = (TP / (TP + FN)),
    FPR = (FP / (FP + TN)),
    FNR = (FN / (FN + TP)),
    FDR = (FP / (FP + TP)),
    PPV = (TP / (TP + FP)),
    NPV = (TN / (TN + FN)),
    TNR = (TN / (TN + FP))  
    )


df_thresh <- NULL
tmp <- df_a_metrics
df_thresh <- rbind(df_thresh,tmp[which.max(tmp$TPR + (1-tmp$FPR) ),])
count_cuttoff <- tmp[which.max(tmp$TPR + (1-tmp$FPR) ),"Threshold"]

tmp <- df_prr_metrics
df_thresh <- rbind(df_thresh,tmp[which.max(tmp$TPR + (1-tmp$FPR) ),])
prr_cuttoff <- tmp[which.max(tmp$TPR + (1-tmp$FPR) ),"Threshold"]

tmp <- df_psm_prr_metrics
df_thresh <- rbind(df_thresh,tmp[which.max(tmp$TPR + (1-tmp$FPR) ),])
psm_prr_cuttoff <- tmp[which.max(tmp$TPR + (1-tmp$FPR) ),"Threshold"]

tmp <- df_rxn_d_cunder_metrics
df_thresh <- rbind(df_thresh,tmp[which.max(tmp$TPR + (1-tmp$FPR) ),])
drug_cunder_cuttoff <- tmp[which.max(tmp$TPR + (1-tmp$FPR) ),"Threshold"]

tmp <- df_rxn_PSd_cunder_metrics
df_thresh <- rbind(df_thresh,tmp[which.max(tmp$TPR + (1-tmp$FPR) ),])
PSd_cunder_cuttoff <- tmp[which.max(tmp$TPR + (1-tmp$FPR) ),"Threshold"]

tmp <- df_rxn_ds_cunder_metrics
df_thresh <- rbind(df_thresh,tmp[which.max(tmp$TPR + (1-tmp$FPR) ),])
drugs_cunder_cuttoff <- tmp[which.max(tmp$TPR + (1-tmp$FPR) ),"Threshold"]

df_thresh

g <- df_thresh %>% 
  gather(Metric,Value,-Statistic,-Stat) %>%  
  filter(!Metric %in% c("Threshold","FP","TP","TN","FN")) %>% 
  ggplot() + 
  geom_bar(
    aes(forcats::fct_reorder(Statistic,Value),Value,fill=Metric),
    stat="identity") + 
  ylim(0,1) + 
  xlab("") +
  facet_wrap(Metric~.,scales="free") + 
  coord_flip() + 
  theme(
    legend.position = "none"
    )

print(g)

ggsave(paste0(out_dir,basename,"_metric_performances_comparison_at_cutoff.png"),
       width=12,height=5)

truth_pred_join$Count_Class <- truth_pred_join$a>count_cuttoff
table(truth_pred_join$Count_Class)

truth_pred_join$PRR_Class <- truth_pred_join$PRR>prr_cuttoff
table(truth_pred_join$PRR_Class)

truth_pred_psm_prr_no_cunder_join$PSM_PRR_Class <- truth_pred_psm_prr_no_cunder_join$PRR>prr_cuttoff
table(truth_pred_psm_prr_no_cunder_join$PSM_PRR_Class)

truth_glm_rx_d_cunder_join$Class <- truth_glm_rx_d_cunder_join$mest>drug_cunder_cuttoff
table(truth_glm_rx_d_cunder_join$Class)

truth_glm_rx_PSd_cunder_join$Class <- truth_glm_rx_PSd_cunder_join$mest>PSd_cunder_cuttoff
table(truth_glm_rx_PSd_cunder_join$Class)

truth_glm_rx_ds_cunder_join$Class <- truth_glm_rx_ds_cunder_join$mest>drugs_cunder_cuttoff
table(truth_glm_rx_ds_cunder_join$Class)

grip <- read_csv("../data/GRiP_Pediatric_ADE_Gold_Standard_List_minimal_joined.csv")

left_join(truth_pred_join %>% 
            select(ATC_concept_name,
                   MedDRA_concept_name,
                   Count_Class) %>% 
            distinct(),
          grip %>% 
            select(MedDRA_concept_name,
                   ATC_concept_name,Control,
                   Level_of_epidemiological_evidence,
                   Population,Classification,Grade) %>% 
            distinct()
          ) %>% 
  arrange(desc(Population))

left_join(truth_pred_join %>% 
            select(ATC_concept_name,
                   MedDRA_concept_name,
                   PRR_Class) %>% 
            distinct(),
          grip %>% 
            select(MedDRA_concept_name,
                   ATC_concept_name,Control,
                   Level_of_epidemiological_evidence,
                   Population,Classification,Grade) %>% 
            distinct()
          ) %>% 
  arrange(desc(Population))

left_join(truth_pred_psm_prr_no_cunder_join %>% 
            select(ATC_concept_name,
                   MedDRA_concept_name,
                   PSM_PRR_Class) %>% 
            distinct(),
          grip %>% 
            select(MedDRA_concept_name,
                   ATC_concept_name,Control,
                   Level_of_epidemiological_evidence,
                   Population,Classification,Grade) %>% 
            distinct()
          ) %>% 
  arrange(desc(Population))

left_join(truth_glm_rx_d_cunder_join %>% 
            select(ATC_concept_name,
                   MedDRA_concept_name,
                   Class) %>% 
            distinct(),
          grip %>% 
            select(MedDRA_concept_name,
                   ATC_concept_name,Control,
                   Level_of_epidemiological_evidence,
                   Population,Classification,Grade) %>% 
            distinct()
          ) %>% 
  arrange(desc(Population))

left_join(truth_glm_rx_ds_cunder_join %>% 
            select(ATC_concept_name,
                   MedDRA_concept_name,
                   Class) %>% 
            distinct(),
          grip %>% 
            select(MedDRA_concept_name,
                   ATC_concept_name,Control,
                   Level_of_epidemiological_evidence,
                   Population,Classification,Grade) %>% 
            distinct()
          ) %>% 
  arrange(desc(Population))


```


## Getting bootstraps of performance metrics from glms

### CV
#### load data

```{r}

truth_all <- fread(paste0("../data/GRiP_Pediatric_ADE_with_generated_negatives_meddra",level,".csv"))

glm_rx_drug_psd_cunder <- fread(paste0("../data/pediatric_reference_",level,"_ADE_glm_with_drug_or_PSd_control_undersampling.csv"),drop = c("V1"))

glm_rx_all_drugs_cunder <- fread(paste0("../data/pediatric_reference_",level,"_ADE_glm_with_drugs_control_undersampling.csv"),drop = c("V1"))

glm_rx_drug_cunder <- 
  glm_rx_drug_psd_cunder[
  model_id=="fd_5cv"]

glm_rx_drug_cunder$atc_concept_id <- as.integer(glm_rx_drug_cunder$atc_concept_id)

glm_rx_drug_cunder$meddra_concept_id <- as.integer(glm_rx_drug_cunder$meddra_concept_id)




glm_rx_PSd_cunder <- 
  glm_rx_drug_psd_cunder[
  model_id=="fPSd_5cv"]

glm_rx_PSd_cunder$atc_concept_id <- sapply(strsplit(glm_rx_PSd_cunder$atc_concept_id,"_"),function(x){x[1]})

glm_rx_PSd_cunder$atc_concept_id <- as.integer(glm_rx_PSd_cunder$atc_concept_id)

glm_rx_PSd_cunder$meddra_concept_id <- as.integer(glm_rx_PSd_cunder$meddra_concept_id)



glm_rx_all_drugs_cunder <- 
  glm_rx_all_drugs_cunder[
  model_id=="fdrugs_5cv"]

glm_rx_all_drugs_cunder$atc_concept_id <- as.integer(glm_rx_all_drugs_cunder$atc_concept_id)

glm_rx_all_drugs_cunder$meddra_concept_id <- as.integer(glm_rx_all_drugs_cunder$meddra_concept_id)


```

```{r}

truth_pred_join <- read_csv(paste0("../data/pediatric_reference_",level,"_ADEs_counts_contigency_table_tests.csv")) %>% 
  filter(a>0) %>% 
  data.table()

truth_glm_rx_PSd_cunder_join <- inner_join(truth_all,glm_rx_PSd_cunder,
                   by=c("ATC_concept_id"="atc_concept_id",
                        "MedDRA_concept_id"="meddra_concept_id")
                   ) %>% 
  select(ATC_concept_name,MedDRA_concept_name,
         Control,bootstrap,
         coefficient) %>% 
  distinct() %>% 
  group_by(ATC_concept_name,MedDRA_concept_name,
         Control) %>% 
  mutate(
    sdest = sd(coefficient),
    mest = mean(coefficient),
    lwr = mest - sdest,
    upr = mest + sdest
  ) %>% 
  ungroup() %>% 
  select(-bootstrap,-coefficient,-sdest) %>% 
  data.table()

truth_glm_rx_d_cunder_join <- inner_join(truth_all,glm_rx_drug_cunder,
                   by=c("ATC_concept_id"="atc_concept_id",
                        "MedDRA_concept_id"="meddra_concept_id")
                   ) %>% 
  select(ATC_concept_name,MedDRA_concept_name,
         Control,bootstrap,
         coefficient) %>% 
  distinct()  %>% 
  group_by(ATC_concept_name,MedDRA_concept_name,
         Control) %>% 
  mutate(
    sdest = sd(coefficient),
    mest = mean(coefficient),
    lwr = mest - sdest,
    upr = mest + sdest
  ) %>% 
  ungroup() %>% 
  select(-bootstrap,-coefficient,-sdest) %>% 
  data.table()

truth_glm_rx_ds_cunder_join <- inner_join(truth_all,glm_rx_all_drugs_cunder,
                   by=c("ATC_concept_id"="atc_concept_id",
                        "MedDRA_concept_id"="meddra_concept_id")
                   ) %>% 
  select(ATC_concept_name,MedDRA_concept_name,
         Control,bootstrap,
         coefficient) %>% 
  distinct() %>% 
  group_by(ATC_concept_name,MedDRA_concept_name,
         Control) %>% 
  mutate(
    sdest = sd(coefficient),
    mest = mean(coefficient),
    lwr = mest - sdest,
    upr = mest + sdest
  ) %>% 
  ungroup() %>% 
  select(-bootstrap,-coefficient,-sdest) %>% 
  data.table()


```

```{r}

table(truth_pred_join$Control)

```

#### Define performance functions

```{r}

vary_phv_threshold <- function(joined,
                               n,
                               param="",
                               drug_col="",rx_col=""){

  tp_cond = paste0(param," > ",n," & Control=='P'")
  fp_cond = paste0(param," > ",n," & Control=='N'")
  fn_cond = paste0(param," <= ",n," & Control=='P'")
  tn_cond = paste0(param," <= ",n," & Control=='N'")
  
  tps <- joined %>% 
    filter_(tp_cond)
  fps <- joined %>% 
    filter_(fp_cond)
  fns <- joined %>% 
    filter_(fn_cond)  
  tns <- joined %>% 
    filter_(tn_cond)
  
  tp_num = tps %>% 
    select(!!drug_col,!!rx_col) %>% 
    n_distinct()
  
  fp_num = fps %>% 
    select(!!drug_col,!!rx_col) %>% 
    n_distinct()
  
  fn_num = fns %>% 
    select(!!drug_col,!!rx_col) %>% 
    n_distinct()

  tn_num = tns %>% 
    select(!!drug_col,!!rx_col) %>% 
    n_distinct()
  
  df <- data.frame(
    "TP" = tp_num,
    "FP" = fp_num,
    "FN" = fn_num,
    "TN" = tn_num,
    "Threshold" = n,
    "Stat" = param
  ) 
  
  df
  
}

```





#### Compare statistic performance

```{r}

stats <- colnames(truth_glm_rx_d_cunder_join)[!colnames(truth_glm_rx_d_cunder_join) %in% c("ATC_concept_name","MedDRA_concept_name","Control")]


thresholds <- c(0,
                unique(truth_glm_rx_d_cunder_join$lwr),
                unique(truth_glm_rx_d_cunder_join$mest),
                unique(truth_glm_rx_d_cunder_join$upr),
                1
                )
thresholds <- thresholds[order(thresholds,decreasing = F)]
thresholds <- thresholds[!is.infinite(thresholds)]
grid <- expand.grid(stats,thresholds)

df_rxn_d <- foreach(i=1:nrow(grid),
        .combine="rbind") %dopar% {
          st = grid[i,1]
          x = grid[i,2]
          tmp <- vary_phv_threshold(
                         truth_glm_rx_d_cunder_join,
                         x,
                         st,
                         drug_col="ATC_concept_name",
                         rx_col="MedDRA_concept_name"
                         )
            }


df_rxn_d["Statistic"] <- "drug"

thresholds <- c(0,
                unique(truth_glm_rx_PSd_cunder_join$lwr),
                unique(truth_glm_rx_PSd_cunder_join$mest),
                unique(truth_glm_rx_PSd_cunder_join$upr),
                1
                )
thresholds <- thresholds[order(thresholds,decreasing = F)]
thresholds <- thresholds[!is.infinite(thresholds)]
grid <- expand.grid(stats,thresholds)

df_rxn_PSd <- foreach(i=1:nrow(grid),
        .combine="rbind") %dopar% {
          s = grid[i,1]
          x = grid[i,2]
          tmp <- vary_phv_threshold(
                         truth_glm_rx_d_cunder_join,
                         x,
                         param=s,
                         drug_col="ATC_concept_name",
                         rx_col="MedDRA_concept_name"
                         )
            }


df_rxn_PSd["Statistic"] <- "propensity score"

thresholds <- c(0,
                unique(truth_glm_rx_ds_cunder_join$lwr),
                unique(truth_glm_rx_ds_cunder_join$mest),
                unique(truth_glm_rx_ds_cunder_join$upr),
                1
                )
thresholds <- thresholds[order(thresholds,decreasing = F)]
thresholds <- thresholds[!is.infinite(thresholds)]
grid <- expand.grid(stats,thresholds)

df_rxn_ds <- foreach(i=1:nrow(grid),
        .combine="rbind") %dopar% {
          s = grid[i,1]
          x = grid[i,2]
          tmp <- vary_phv_threshold(
                         truth_glm_rx_ds_cunder_join,
                         x,
                         param=s,
                         drug_col="ATC_concept_name",
                         rx_col="MedDRA_concept_name"
                         )
            }


df_rxn_ds["Statistic"] <- "drug given all other drugs"

g <- 
  bind_rows(
    df_rxn_d,
    df_rxn_PSd,
    df_rxn_ds
) %>%  
  group_by(Statistic) %>% 
  mutate(
    Sensitivity = TP / (TP + FN),
    Specificity = (FP / (FP + TN))
  ) %>%
  ungroup() %>% 
  ggplot(aes(Specificity,Sensitivity,color=Statistic)) +
  scale_color_brewer(palette="Set1") +
  geom_point() +
  geom_line() +
  ylab("Sensitivity") +
  xlab("1 - Specificity") +
  xlim(0,1) +
  ylim(0,1)
  
print(g)

ggsave(paste0(out_dir,basename,"_ROC_performance_glm_CIs_CV.png"),
       width=10,height=5)

g <- 
  bind_rows(
    df_rxn_d,
    df_rxn_PSd,
    df_rxn_ds
) %>%  
  group_by(Statistic) %>% 
  mutate(
    Precision = TP / (TP + FP),
    Recall = (TP / (TP + FN))
  ) %>%
  ungroup() %>% 
  ggplot(aes(Precision,Recall,color=Statistic)) +
  scale_color_brewer(palette="Set1") +
  geom_point() +
  geom_line() +
  ylab("Recall") +
  xlab("Precision") +
  xlim(0,1) +
  ylim(0,1)
  
print(g)

ggsave(paste0(out_dir,basename,"_precision_recall_performance_glm_CIs_CV.png"),
       width=10,height=5)

```

#### Scores

```{r}

df <- bind_rows(
  df_rxn_d,
  df_rxn_PSd,
  df_rxn_ds
) %>%  
  arrange(Threshold) %>% 
  group_by(Statistic,Stat) %>% 
  mutate(
    TPR = (TP / (TP + FN)),
    FPR = (FP / (FP + TN)),
    FNR = (FN / (FN + TP)),
    FDR = (FP / (FP + TP)),
    PPV = (TP / (TP + FP)),
    NPV = (TN / (TN + FN)),
    TNR = (TN / (TN + FP))
  )

simple_auc <- function(TPR, FPR){
  # inputs already sorted, best scores first 
  dFPR <- c(diff(FPR), 0)
  dTPR <- c(diff(TPR), 0)
  sum(TPR * dFPR) + sum(dTPR * dFPR)/2
}

grid <- expand.grid(unique(df$Statistic),unique(df$Stat))

df_scores_auc <- 
  foreach(i=1:nrow(grid),
        .combine="rbind") %dopar% {
          S <- grid[i,1] %>% as.character()
          s <- grid[i,2] %>% as.character()
  tmp <- df %>% 
    filter(Statistic==S,Stat==s) %>% 
    arrange(desc(Stat)) %>% 
    drop_na()
  tpr <- tmp$TPR[order(tmp$TPR)]
  fpr <- tmp$FPR[order(tmp$FPR)]
  c(S,s,"AUROC",simple_auc(tpr,fpr))
        }

df_scores_apr <- 
  foreach(i=1:nrow(grid),
        .combine="rbind") %dopar% {
          S <- grid[i,1] %>% as.character()
          s <- grid[i,2] %>% as.character()
  tmp <- df %>% 
    filter(Statistic==S,Stat==s) %>% 
    arrange(desc(Stat)) %>% 
    drop_na()
  recall <- tmp$TPR[order(tmp$TPR)]
  precision <- tmp$PPV[order(tmp$PPV)]
  c(S,s,"AUPRC",simple_auc(recall,precision))
}

df_scores <- as_tibble(
  rbind(df_scores_auc,df_scores_apr),
  .name_repair = "minimal")
colnames(df_scores) <- c("Detection","Stat","Metric","Score")
df_scores$Score <- as.numeric(df_scores$Score)

g <- df_scores  %>% 
  spread(Stat,Score) %>% 
  ggplot(aes(x=forcats::fct_reorder(Detection,mest),
               ymin=lwr,ymax=upr,y=mest,
               color=Detection)) +
  geom_errorbar(stat="identity",width=.5) +
  scale_color_brewer(palette = "Set1") +
  facet_grid(Metric~.) +
  xlab("") +
  ylim(0,1) +
  coord_flip() +
  theme(
    legend.position = "none"
  )

print(g)

ggsave(paste0(out_dir,basename,"_aumetric_glm_CIs_performances_comparison_CV.png"),
       width=10,height=5)

g <- df %>% 
  gather(Metric, Value,
         -Threshold,-Statistic,-Stat) %>% 
  filter(!(Metric %in% c("TP","TN","FP","FN"))) %>% 
  ggplot(aes(Threshold,Value,
                 color=Statistic,
                 group=Statistic)) +
  geom_point() +
  geom_path() +
  facet_wrap(~Metric) +
  scale_color_brewer(palette="Set1") +
  scale_x_log10()


print(g)

ggsave(paste0(out_dir,basename,"_glm_CIs_metric_performances_comparison_CV.png"),
       width=10,height=5)


g <- df %>% 
  gather(Metric, Value,
         -Threshold,-Statistic,-Stat) %>% 
  filter((Metric %in% c("PPV","TPR"))) %>% 
  ggplot(aes(Threshold,Value,
                 color=Statistic,
                 group=Statistic)) +
  geom_point() +
  geom_path() +
  facet_wrap(~Metric) +
  scale_color_brewer(palette="Set1") +
  scale_x_log10()


print(g)

ggsave(paste0(out_dir,basename,"_glm_CIs_PPV_TPR_performance_comparison_CV.png"),
       width=10,height=5)

g <- df %>% 
  gather(Metric, Value,
         -Threshold,-Statistic,-Stat) %>% 
  filter((Metric %in% c("PPV","NPV","FPR","TPR"))) %>% 
  ggplot(aes(Threshold,Value,
                 color=Metric,
                 group=Metric)) +
  geom_point() +
  geom_path() +
  facet_wrap(~Statistic) +
  scale_color_brewer(palette="Set1") +
  scale_x_log10()

print(g)

```

#### Cutoffs

```{r}

df_rxn_PSd_cunder_metrics <- df_rxn_PSd %>% 
  mutate(
    TPR = (TP / (TP + FN)),
    FPR = (FP / (FP + TN)),
    FNR = (FN / (FN + TP)),
    FDR = (FP / (FP + TP)),
    PPV = (TP / (TP + FP)),
    NPV = (TN / (TN + FN)),
    TNR = (TN / (TN + FP))  
    )

df_rxn_d_cunder_metrics <- df_rxn_d %>% 
  mutate(
    TPR = (TP / (TP + FN)),
    FPR = (FP / (FP + TN)),
    FNR = (FN / (FN + TP)),
    FDR = (FP / (FP + TP)),
    PPV = (TP / (TP + FP)),
    NPV = (TN / (TN + FN)),
    TNR = (TN / (TN + FP))  
    )

df_rxn_ds_cunder_metrics <- df_rxn_ds %>% 
  mutate(
    TPR = (TP / (TP + FN)),
    FPR = (FP / (FP + TN)),
    FNR = (FN / (FN + TP)),
    FDR = (FP / (FP + TP)),
    PPV = (TP / (TP + FP)),
    NPV = (TN / (TN + FN)),
    TNR = (TN / (TN + FP))  
    )


df_thresh <- NULL
tmp <- df_rxn_d_cunder_metrics
df_thresh <- rbind(df_thresh,tmp[which.max(tmp$TPR + (1-tmp$FPR) ),])
drug_cunder_cuttoff <- tmp[which.max(tmp$TPR + (1-tmp$FPR) ),"Threshold"]

tmp <- df_rxn_PSd_cunder_metrics
df_thresh <- rbind(df_thresh,tmp[which.max(tmp$TPR + (1-tmp$FPR) ),])
PSd_cunder_cuttoff <- tmp[which.max(tmp$TPR + (1-tmp$FPR) ),"Threshold"]

tmp <- df_rxn_ds_cunder_metrics
df_thresh <- rbind(df_thresh,tmp[which.max(tmp$TPR + (1-tmp$FPR) ),])
drugs_cunder_cuttoff <- tmp[which.max(tmp$TPR + (1-tmp$FPR) ),"Threshold"]

df_thresh

truth_glm_rx_d_cunder_join$Class <- truth_glm_rx_d_cunder_join$mest>drug_cunder_cuttoff
table(truth_glm_rx_d_cunder_join$Class)

truth_glm_rx_PSd_cunder_join$Class <- truth_glm_rx_PSd_cunder_join$mest>PSd_cunder_cuttoff
table(truth_glm_rx_PSd_cunder_join$Class)

truth_glm_rx_ds_cunder_join$Class <- truth_glm_rx_ds_cunder_join$mest>drugs_cunder_cuttoff
table(truth_glm_rx_ds_cunder_join$Class)

grip <- read_csv("../data/GRiP_Pediatric_ADE_Gold_Standard_List_minimal_joined.csv")


left_join(truth_glm_rx_d_cunder_join %>% 
            select(ATC_concept_name,
                   MedDRA_concept_name,
                   Class) %>% 
            distinct(),
          grip %>% 
            select(MedDRA_concept_name,
                   ATC_concept_name,Control,
                   Level_of_epidemiological_evidence,
                   Population,Classification,Grade) %>% 
            distinct()
          ) %>% 
  arrange(desc(Population))

left_join(truth_glm_rx_ds_cunder_join %>% 
            select(ATC_concept_name,
                   MedDRA_concept_name,
                   Class) %>% 
            distinct(),
          grip %>% 
            select(MedDRA_concept_name,
                   ATC_concept_name,Control,
                   Level_of_epidemiological_evidence,
                   Population,Classification,Grade) %>% 
            distinct()
          ) %>% 
  arrange(desc(Population))


```

### no CV
#### load data

```{r}

truth_all <- fread(paste0("../data/GRiP_Pediatric_ADE_with_generated_negatives_meddra",level,".csv"))

glm_rx_drug_psd_cunder <- fread(paste0("../data/pediatric_reference_",level,"_ADE_glm_with_drug_or_PSd_control_undersampling.csv"),drop = c("V1"))

glm_rx_all_drugs_cunder <- fread(paste0("../data/pediatric_reference_",level,"_ADE_glm_with_drugs_control_undersampling.csv"),drop = c("V1"))

glm_rx_drug_cunder <- 
  glm_rx_drug_psd_cunder[
  model_id=="fd"]

glm_rx_drug_cunder$atc_concept_id <- as.integer(glm_rx_drug_cunder$atc_concept_id)

glm_rx_drug_cunder$meddra_concept_id <- as.integer(glm_rx_drug_cunder$meddra_concept_id)




glm_rx_PSd_cunder <- 
  glm_rx_drug_psd_cunder[
  model_id=="fPSd"]

glm_rx_PSd_cunder$atc_concept_id <- sapply(strsplit(glm_rx_PSd_cunder$atc_concept_id,"_"),function(x){x[1]})

glm_rx_PSd_cunder$atc_concept_id <- as.integer(glm_rx_PSd_cunder$atc_concept_id)

glm_rx_PSd_cunder$meddra_concept_id <- as.integer(glm_rx_PSd_cunder$meddra_concept_id)



glm_rx_all_drugs_cunder <- 
  glm_rx_all_drugs_cunder[
  model_id=="fdrugs"]

glm_rx_all_drugs_cunder$atc_concept_id <- as.integer(glm_rx_all_drugs_cunder$atc_concept_id)

glm_rx_all_drugs_cunder$meddra_concept_id <- as.integer(glm_rx_all_drugs_cunder$meddra_concept_id)


```

```{r}

truth_pred_join <- read_csv(paste0("../data/pediatric_reference_",level,"_ADEs_counts_contigency_table_tests.csv")) %>% 
  filter(a>0) %>% 
  data.table()

truth_glm_rx_PSd_cunder_join <- inner_join(truth_all,glm_rx_PSd_cunder,
                   by=c("ATC_concept_id"="atc_concept_id",
                        "MedDRA_concept_id"="meddra_concept_id")
                   ) %>% 
  select(ATC_concept_name,MedDRA_concept_name,
         Control,bootstrap,
         coefficient) %>% 
  distinct() %>% 
  group_by(ATC_concept_name,MedDRA_concept_name,
         Control) %>% 
  mutate(
    sdest = sd(coefficient),
    mest = mean(coefficient),
    lwr = mest - sdest,
    upr = mest + sdest
  ) %>% 
  ungroup() %>% 
  select(-bootstrap,-coefficient,-sdest) %>% 
  data.table()

truth_glm_rx_d_cunder_join <- inner_join(truth_all,glm_rx_drug_cunder,
                   by=c("ATC_concept_id"="atc_concept_id",
                        "MedDRA_concept_id"="meddra_concept_id")
                   ) %>% 
  select(ATC_concept_name,MedDRA_concept_name,
         Control,bootstrap,
         coefficient) %>% 
  distinct()  %>% 
  group_by(ATC_concept_name,MedDRA_concept_name,
         Control) %>% 
  mutate(
    sdest = sd(coefficient),
    mest = mean(coefficient),
    lwr = mest - sdest,
    upr = mest + sdest
  ) %>% 
  ungroup() %>% 
  select(-bootstrap,-coefficient,-sdest) %>% 
  data.table()

truth_glm_rx_ds_cunder_join <- inner_join(truth_all,glm_rx_all_drugs_cunder,
                   by=c("ATC_concept_id"="atc_concept_id",
                        "MedDRA_concept_id"="meddra_concept_id")
                   ) %>% 
  select(ATC_concept_name,MedDRA_concept_name,
         Control,bootstrap,
         coefficient) %>% 
  distinct() %>% 
  group_by(ATC_concept_name,MedDRA_concept_name,
         Control) %>% 
  mutate(
    sdest = sd(coefficient),
    mest = mean(coefficient),
    lwr = mest - sdest,
    upr = mest + sdest
  ) %>% 
  ungroup() %>% 
  select(-bootstrap,-coefficient,-sdest) %>% 
  data.table()


```

```{r}

table(truth_pred_join$Control)

```

#### Define performance functions

```{r}

vary_phv_threshold <- function(joined,
                               n,
                               param="",
                               drug_col="",rx_col=""){

  tp_cond = paste0(param," > ",n," & Control=='P'")
  fp_cond = paste0(param," > ",n," & Control=='N'")
  fn_cond = paste0(param," <= ",n," & Control=='P'")
  tn_cond = paste0(param," <= ",n," & Control=='N'")
  
  tps <- joined %>% 
    filter_(tp_cond)
  fps <- joined %>% 
    filter_(fp_cond)
  fns <- joined %>% 
    filter_(fn_cond)  
  tns <- joined %>% 
    filter_(tn_cond)
  
  tp_num = tps %>% 
    select(!!drug_col,!!rx_col) %>% 
    n_distinct()
  
  fp_num = fps %>% 
    select(!!drug_col,!!rx_col) %>% 
    n_distinct()
  
  fn_num = fns %>% 
    select(!!drug_col,!!rx_col) %>% 
    n_distinct()

  tn_num = tns %>% 
    select(!!drug_col,!!rx_col) %>% 
    n_distinct()
  
  df <- data.frame(
    "TP" = tp_num,
    "FP" = fp_num,
    "FN" = fn_num,
    "TN" = tn_num,
    "Threshold" = n,
    "Stat" = param
  ) 
  
  df
  
}

```





#### Compare statistic performance

```{r}

stats <- colnames(truth_glm_rx_d_cunder_join)[!colnames(truth_glm_rx_d_cunder_join) %in% c("ATC_concept_name","MedDRA_concept_name","Control")]


thresholds <- c(0,
                unique(truth_glm_rx_d_cunder_join$lwr),
                unique(truth_glm_rx_d_cunder_join$mest),
                unique(truth_glm_rx_d_cunder_join$upr),
                1
                )
thresholds <- thresholds[order(thresholds,decreasing = F)]
thresholds <- thresholds[!is.infinite(thresholds)]
grid <- expand.grid(stats,thresholds)

df_rxn_d <- foreach(i=1:nrow(grid),
        .combine="rbind") %dopar% {
          st = grid[i,1]
          x = grid[i,2]
          tmp <- vary_phv_threshold(
                         truth_glm_rx_d_cunder_join,
                         x,
                         st,
                         drug_col="ATC_concept_name",
                         rx_col="MedDRA_concept_name"
                         )
            }


df_rxn_d["Statistic"] <- "drug"

thresholds <- c(0,
                unique(truth_glm_rx_PSd_cunder_join$lwr),
                unique(truth_glm_rx_PSd_cunder_join$mest),
                unique(truth_glm_rx_PSd_cunder_join$upr),
                1
                )
thresholds <- thresholds[order(thresholds,decreasing = F)]
thresholds <- thresholds[!is.infinite(thresholds)]
grid <- expand.grid(stats,thresholds)

df_rxn_PSd <- foreach(i=1:nrow(grid),
        .combine="rbind") %dopar% {
          s = grid[i,1]
          x = grid[i,2]
          tmp <- vary_phv_threshold(
                         truth_glm_rx_d_cunder_join,
                         x,
                         param=s,
                         drug_col="ATC_concept_name",
                         rx_col="MedDRA_concept_name"
                         )
            }


df_rxn_PSd["Statistic"] <- "propensity score"

thresholds <- c(0,
                unique(truth_glm_rx_ds_cunder_join$lwr),
                unique(truth_glm_rx_ds_cunder_join$mest),
                unique(truth_glm_rx_ds_cunder_join$upr),
                1
                )
thresholds <- thresholds[order(thresholds,decreasing = F)]
thresholds <- thresholds[!is.infinite(thresholds)]
grid <- expand.grid(stats,thresholds)

df_rxn_ds <- foreach(i=1:nrow(grid),
        .combine="rbind") %dopar% {
          s = grid[i,1]
          x = grid[i,2]
          tmp <- vary_phv_threshold(
                         truth_glm_rx_ds_cunder_join,
                         x,
                         param=s,
                         drug_col="ATC_concept_name",
                         rx_col="MedDRA_concept_name"
                         )
            }


df_rxn_ds["Statistic"] <- "drug given all other drugs"

g <- 
  bind_rows(
    df_rxn_d,
    df_rxn_PSd,
    df_rxn_ds
) %>%  
  group_by(Statistic) %>% 
  mutate(
    Sensitivity = TP / (TP + FN),
    Specificity = (FP / (FP + TN))
  ) %>%
  ungroup() %>% 
  ggplot(aes(Specificity,Sensitivity,color=Statistic)) +
  scale_color_brewer(palette="Set1") +
  geom_point() +
  geom_line() +
  ylab("Sensitivity") +
  xlab("1 - Specificity") +
  xlim(0,1) +
  ylim(0,1)
  
print(g)

ggsave(paste0(out_dir,basename,"_ROC_performance_glm_CIs_CV.png"),
       width=10,height=5)

g <- 
  bind_rows(
    df_rxn_d,
    df_rxn_PSd,
    df_rxn_ds
) %>%  
  group_by(Statistic) %>% 
  mutate(
    Precision = TP / (TP + FP),
    Recall = (TP / (TP + FN))
  ) %>%
  ungroup() %>% 
  ggplot(aes(Precision,Recall,color=Statistic)) +
  scale_color_brewer(palette="Set1") +
  geom_point() +
  geom_line() +
  ylab("Recall") +
  xlab("Precision") +
  xlim(0,1) +
  ylim(0,1)
  
print(g)

ggsave(paste0(out_dir,basename,"_precision_recall_performance_glm_CIs_noCV.png"),
       width=10,height=5)

```

#### Scores

```{r}

df <- bind_rows(
  df_rxn_d,
  df_rxn_PSd,
  df_rxn_ds
) %>%  
  arrange(Threshold) %>% 
  group_by(Statistic,Stat) %>% 
  mutate(
    TPR = (TP / (TP + FN)),
    FPR = (FP / (FP + TN)),
    FNR = (FN / (FN + TP)),
    FDR = (FP / (FP + TP)),
    PPV = (TP / (TP + FP)),
    NPV = (TN / (TN + FN)),
    TNR = (TN / (TN + FP))
  )

simple_auc <- function(TPR, FPR){
  # inputs already sorted, best scores first 
  dFPR <- c(diff(FPR), 0)
  dTPR <- c(diff(TPR), 0)
  sum(TPR * dFPR) + sum(dTPR * dFPR)/2
}

grid <- expand.grid(unique(df$Statistic),unique(df$Stat))

df_scores_auc <- 
  foreach(i=1:nrow(grid),
        .combine="rbind") %dopar% {
          S <- grid[i,1] %>% as.character()
          s <- grid[i,2] %>% as.character()
  tmp <- df %>% 
    filter(Statistic==S,Stat==s) %>% 
    arrange(desc(Stat)) %>% 
    drop_na()
  tpr <- tmp$TPR[order(tmp$TPR)]
  fpr <- tmp$FPR[order(tmp$FPR)]
  c(S,s,"AUROC",simple_auc(tpr,fpr))
        }

df_scores_apr <- 
  foreach(i=1:nrow(grid),
        .combine="rbind") %dopar% {
          S <- grid[i,1] %>% as.character()
          s <- grid[i,2] %>% as.character()
  tmp <- df %>% 
    filter(Statistic==S,Stat==s) %>% 
    arrange(desc(Stat)) %>% 
    drop_na()
  recall <- tmp$TPR[order(tmp$TPR)]
  precision <- tmp$PPV[order(tmp$PPV)]
  c(S,s,"AUPRC",simple_auc(recall,precision))
}

df_scores <- as_tibble(
  rbind(df_scores_auc,df_scores_apr),
  .name_repair = "minimal")
colnames(df_scores) <- c("Detection","Stat","Metric","Score")
df_scores$Score <- as.numeric(df_scores$Score)

g <- df_scores  %>% 
  spread(Stat,Score) %>% 
  ggplot(aes(x=forcats::fct_reorder(Detection,mest),
               ymin=lwr,ymax=upr,y=mest,
               color=Detection)) +
  geom_errorbar(stat="identity",width=.5) +
  scale_color_brewer(palette = "Set1") +
  facet_grid(Metric~.) +
  xlab("") +
  ylim(0,1) +
  coord_flip() +
  theme(
    legend.position = "none"
  )

print(g)

ggsave(paste0(out_dir,basename,"_aumetric_glm_CIs_performances_comparison_noCV.png"),
       width=10,height=5)

g <- df %>% 
  gather(Metric, Value,
         -Threshold,-Statistic,-Stat) %>% 
  filter(!(Metric %in% c("TP","TN","FP","FN"))) %>% 
  ggplot(aes(Threshold,Value,
                 color=Statistic,
                 group=Statistic)) +
  geom_point() +
  geom_path() +
  facet_wrap(~Metric) +
  scale_color_brewer(palette="Set1") +
  scale_x_log10()


print(g)

ggsave(paste0(out_dir,basename,"_glm_CIs_metric_performances_comparison_noCV.png"),
       width=10,height=5)


g <- df %>% 
  gather(Metric, Value,
         -Threshold,-Statistic,-Stat) %>% 
  filter((Metric %in% c("PPV","TPR"))) %>% 
  ggplot(aes(Threshold,Value,
                 color=Statistic,
                 group=Statistic)) +
  geom_point() +
  geom_path() +
  facet_wrap(~Metric) +
  scale_color_brewer(palette="Set1") +
  scale_x_log10()


print(g)

ggsave(paste0(out_dir,basename,"_glm_CIs_PPV_TPR_performance_comparison_noCV.png"),
       width=10,height=5)

g <- df %>% 
  gather(Metric, Value,
         -Threshold,-Statistic,-Stat) %>% 
  filter((Metric %in% c("PPV","NPV","FPR","TPR"))) %>% 
  ggplot(aes(Threshold,Value,
                 color=Metric,
                 group=Metric)) +
  geom_point() +
  geom_path() +
  facet_wrap(~Statistic) +
  scale_color_brewer(palette="Set1") +
  scale_x_log10()

print(g)

```





#### Cutoffs

```{r}

df_rxn_PSd_cunder_metrics <- df_rxn_PSd %>% 
  mutate(
    TPR = (TP / (TP + FN)),
    FPR = (FP / (FP + TN)),
    FNR = (FN / (FN + TP)),
    FDR = (FP / (FP + TP)),
    PPV = (TP / (TP + FP)),
    NPV = (TN / (TN + FN)),
    TNR = (TN / (TN + FP))  
    )

df_rxn_d_cunder_metrics <- df_rxn_d %>% 
  mutate(
    TPR = (TP / (TP + FN)),
    FPR = (FP / (FP + TN)),
    FNR = (FN / (FN + TP)),
    FDR = (FP / (FP + TP)),
    PPV = (TP / (TP + FP)),
    NPV = (TN / (TN + FN)),
    TNR = (TN / (TN + FP))  
    )

df_rxn_ds_cunder_metrics <- df_rxn_ds %>% 
  mutate(
    TPR = (TP / (TP + FN)),
    FPR = (FP / (FP + TN)),
    FNR = (FN / (FN + TP)),
    FDR = (FP / (FP + TP)),
    PPV = (TP / (TP + FP)),
    NPV = (TN / (TN + FN)),
    TNR = (TN / (TN + FP))  
    )


df_thresh <- NULL
tmp <- df_rxn_d_cunder_metrics
df_thresh <- rbind(df_thresh,tmp[which.max(tmp$TPR + (1-tmp$FPR) ),])
drug_cunder_cuttoff <- tmp[which.max(tmp$TPR + (1-tmp$FPR) ),"Threshold"]

tmp <- df_rxn_PSd_cunder_metrics
df_thresh <- rbind(df_thresh,tmp[which.max(tmp$TPR + (1-tmp$FPR) ),])
PSd_cunder_cuttoff <- tmp[which.max(tmp$TPR + (1-tmp$FPR) ),"Threshold"]

tmp <- df_rxn_ds_cunder_metrics
df_thresh <- rbind(df_thresh,tmp[which.max(tmp$TPR + (1-tmp$FPR) ),])
drugs_cunder_cuttoff <- tmp[which.max(tmp$TPR + (1-tmp$FPR) ),"Threshold"]

df_thresh

truth_glm_rx_d_cunder_join$Class <- truth_glm_rx_d_cunder_join$mest>drug_cunder_cuttoff
table(truth_glm_rx_d_cunder_join$Class)

truth_glm_rx_PSd_cunder_join$Class <- truth_glm_rx_PSd_cunder_join$mest>PSd_cunder_cuttoff
table(truth_glm_rx_PSd_cunder_join$Class)

truth_glm_rx_ds_cunder_join$Class <- truth_glm_rx_ds_cunder_join$mest>drugs_cunder_cuttoff
table(truth_glm_rx_ds_cunder_join$Class)

grip <- read_csv("../data/GRiP_Pediatric_ADE_Gold_Standard_List_minimal_joined.csv")


left_join(truth_glm_rx_d_cunder_join %>% 
            select(ATC_concept_name,
                   MedDRA_concept_name,
                   Class) %>% 
            distinct(),
          grip %>% 
            select(MedDRA_concept_name,
                   ATC_concept_name,Control,
                   Level_of_epidemiological_evidence,
                   Population,Classification,Grade) %>% 
            distinct()
          ) %>% 
  arrange(desc(Population))

left_join(truth_glm_rx_ds_cunder_join %>% 
            select(ATC_concept_name,
                   MedDRA_concept_name,
                   Class) %>% 
            distinct(),
          grip %>% 
            select(MedDRA_concept_name,
                   ATC_concept_name,Control,
                   Level_of_epidemiological_evidence,
                   Population,Classification,Grade) %>% 
            distinct()
          ) %>% 
  arrange(desc(Population))


```








